Tables

### 2019-05-01 code/tables.rmd
Added code to manually transform into tetrachoric correlations
Problem with some variance being zero, which doesn't work for meta-analysis. Will next try metafor's computations instead.
Transform everything  except SE effect using metafor::escalc instead
Change tau2 and CI in table 3 to have 4 digits after decimal

```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_power) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(tau2_ci.ub, 2), nsmall = 2)), "]")) %>% 
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau2, tau2_ci, zero, small, medium, large)

@@

##Table 3
###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
```{r heterogeneity-table, cache = TRUE}
#library(kableExtra)

>>>>

##Table 3
###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_power) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 4), nsmall = 4)), ", ", trimws(format(round(tau2_ci.ub, 4), nsmall = 4)), "]"),
         tau2 = format(round(tau2, 4), nsmall = 4)) %>% #rounded here instead of in table function because should have 4 digits
  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau2, tau2_ci, zero, small, medium, large)

@@

```{r heterogeneity-table, cache = TRUE}
#library(kableExtra)
